The imputation methods big test

### 2020-04-25 pd2.Rmd

```{r warning=FALSE}
  library(knitr)
  results <- c(list(0),list(0),list(0),list(0),list(0))
  results[[1]] <- readRDS('./part_results/res1.rds')
  results[[2]] <- readRDS('./part_results/res2.rds')
  results[[3]] <- readRDS('./part_results/res3.rds')
  results[[4]] <- readRDS('./part_results/res4.rds')
  results[[5]] <- readRDS('./part_results/res5.rds')
  result_table <- function(ds_it){
    d <- data.frame(matrix(ncol = 7, nrow = 0))
    colnames(d) <- c("imputation", "accuracy", "precision", "recall", "f1", "imp_time", "mod_time")
    for (i in 1:length(imputations)){
      if (length(results[[i]][[ds_it]]) != 1){ # length equal 1 means "ERROR" was generated in partial results 
        d[i,] <- c(results[[i]][[ds_it]]$imp_method,
               round(as.numeric(results[[i]][[ds_it]]$classification_report$accuracy),3),   
               round(as.numeric(results[[i]][[ds_it]]$classification_report$precision),3),
               round(as.numeric(results[[i]][[ds_it]]$classification_report$recall),3),
               round(as.numeric(results[[i]][[ds_it]]$classification_report$f1),3),
               round(as.numeric(results[[i]][[ds_it]]$imputation_time),3),
               round(as.numeric(results[[i]][[ds_it]]$modelling_time),3)) 
      }
    }
    d
}
  # change i bound to number of datasets 
  for (i in c(1,2,3,5,6,7,8,9)){
    kable(result_table(i), caption = paste("Dataset id: ", results[[1]][[i]]$dataset_id, sep = ""))
  }

>>>>

```{r warning=FALSE}
  library(knitr)
  results <- c(list(0),list(0),list(0),list(0),list(0))
  results[[1]] <- readRDS('./part_results/res1.rds')
  results[[2]] <- readRDS('./part_results/res2.rds')
  results[[3]] <- readRDS('./part_results/res3.rds')
  results[[4]] <- readRDS('./part_results/res4.rds')
  results[[5]] <- readRDS('./part_results/res5.rds')
  result_table <- function(ds_it){
    d <- data.frame(matrix(ncol = 7, nrow = 0))
    colnames(d) <- c("imputation", "accuracy", "precision", "recall", "f1", "imp_time", "mod_time")
    for (i in 1:length(imputations)){
      if (length(results[[i]][[ds_it]]) != 1){ # length equal 1 means "ERROR" was generated in partial results 
        d[i,] <- c(results[[i]][[ds_it]]$imp_method,
               round(as.numeric(results[[i]][[ds_it]]$classification_report$accuracy),3),   
               round(as.numeric(results[[i]][[ds_it]]$classification_report$precision),3),
               round(as.numeric(results[[i]][[ds_it]]$classification_report$recall),3),
               round(as.numeric(results[[i]][[ds_it]]$classification_report$f1),3),
               round(as.numeric(results[[i]][[ds_it]]$imputation_time),3),
               round(as.numeric(results[[i]][[ds_it]]$modelling_time),3)) 
      }
      else{ # for error input imputation name
        if (i==3){
          d[i,1] <- "imputation_fun_mice" 
        }
        if (i==4){
          d[i,1] <- "imputation_fun_missForest" 
        }
        if (i==5){
          d[i,1] <- "imputation_fun_vim" 
        }
      }
    }
    d
}
  # change i bound to number of datasets 
  for (i in c(1,2,3,5,6,7,8,9)){
    kable(result_table(i), caption = paste("Dataset id: ", results[[1]][[i]]$dataset_id, sep = ""))
  }
